Redundant calibration as a complex optimization problem

### 2016-12-14 paper.tex
added some text to intro

\section{Introduction}

>>>>

\section{Introduction}
Calibration is the procedure by which we remove the instrumental and environmental iduced errors from our intereferometric data. We normally model 
the propogation effects This is normally accomplished using a 
least-squares solver, i.e. we find the propogation effects (antenna gains) that minimizes the difference betweem our observed and predicted visibilities \citep{RIME1}. There are two recent developments
in Calibration approaches that are worth
